Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-29 ms.tex
Some more modifications to the mdot_Ia expression.

What is the effect of the Ia radius?  Between subsequent supernovae, stars release a gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \sim M_{\rm g}\sigma^{2}$.  Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm Ia})^{2}/2\sigma^{2} \gtrsim 1$.  Hence Ia SN can in principle dynamically clear out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.  Thus, even in cases when $r_{\rm s} > r_{\rm Ia}$, the SMBH accretion rate is limited to the value set by substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]) for $r_{\rm s}$ in the derivation of equation $\ref{eq:eddr_analytic}$, i.e.  
\begin{eqnarray}
\left.\frac{\dot{M}}{\dot{M}_{\rm edd}}\right|_{\rm max} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
 && \begin{cases}
    4.5 \times 10^{-4} M_{\bullet,8}^{-1.33}(\tau_{\star}/t_{\rm h})^{1.1}
   & \text{core} \\
    2.2 \times 10^{-4} \Mbheight^{-0.84}(\tau_{\star}/t_{\rm h})^{0.7}   & \text{cusp}.
  \end{cases}
  \label{eq:eddr_Ia}
\end{eqnarray}
{\bf AG: Fixed this expression. I will check again! Ia accretion rate should
  increase with time, as in the burst limit the Ia rate would decline
  with time, so the Ia radius would move outwards (need more volume to
  get a supernova per dynamical time.}

>>>>

What is the effect of the Ia radius?  Between subsequent supernovae, stars release a gaseous mass $M_{\rm g} \approx \eta M_{\star}\tau_{\rm Ia}/t_{\rm h}$ interior to the Ia radius, which is gravitationally bound to the SMBH by an energy $E_{\rm bind} \sim M_{\rm g}\sigma^{2}$.  Thus, according to the above definitions, $E_{\rm Ia}/E_{\rm bind} \sim (v_{w}^{\rm Ia})^{2}/2\sigma^{2} \gtrsim 1$.  Hence Ia SN can in principle dynamically clear out gas from radii $\sim r_{\rm Ia} \gtrsim r_{\rm s}$.  Thus, even in cases when $r_{\rm s} > r_{\rm Ia}$, the SMBH accretion rate is limited to the value set by substituting the Ia radius $r_{\rm Ia}$ (eq.~[\ref{eq:rIa}]) for $r_{\rm s}$ in the derivation of equation $\ref{eq:eddr_analytic}$, i.e.  
\begin{eqnarray}
\left.\frac{\dot{M}}{\dot{M}_{\rm edd}}\right|_{\rm max} &\approx& \frac{\eta M_{\bullet}}{\dot{M}_{\rm edd} t_{\rm h}}\left(\frac{R_{\rm Ia}}{R_{\rm soi}}\right)^{2-\Gamma} \approx \nonumber \\
 && \begin{cases}
    4.5 \times 10^{-4} M_{\bullet,8}^{-1.33}(\tau_{\star}/t_{\rm h})^{-0.2}
   & \text{core} \\
    2.2 \times 10^{-4} \Mbheight^{-0.84}(\tau_{\star}/t_{\rm h})^{-0.6}   & \text{cusp}.
  \end{cases}
  \label{eq:eddr_Ia}
\end{eqnarray}
{\bf AG: Changed this expression somewhat from that of BDM (slightly
  different scaling relations were used?). I will
  check again! Note that the time dependence of eta~t$^{-1.3}$ is
  folded in above.}
